---
title: "Duck Stamp Competition Analysis"
format: html

embed-resources: true
---

# 2024 Federal Duck Stamp Competition: An Analysis

```{r}
#| echo: false
#| output: false

library(tidyverse)
library(ggplot2)
library(readxl)

ducks <- read_excel("2024 Duck Stamp Contest.xlsx")
```

## Which species were most popular among artists?

```{r}
#| echo: false

ducks |>
  filter(Species %in% c("hooded merganser", "northern shoveler", "spectacled eider", "brant", "greater scaup")) |>
  group_by(Species) |>
  summarize(
    count = n(),
    percent = (n() / 239) * 100) |>
  arrange(desc(count))
  
```
The hooded merganser was by far the most common choice for artists to depict, accounting for nearly half of all entries.

## Which species were most popular with the judges?

### Round 1:

```{r}
#| echo: false

ducks |>
  rename("totscorer1" = "Total score R1") |>
  mutate(
    r1pass = if_else(
      condition = totscorer1 >= 3,
      true = 1,
      false = 0
    )
  ) |>
  filter(Species %in% c("hooded merganser", "northern shoveler", "spectacled eider", "brant", "greater scaup")) |>
  group_by(Species) |>
  summarize(
    meanscore = mean(totscorer1), 
    passrate = mean(r1pass)) |>
  arrange(desc(passrate))

```
Greater scaups were most likely to make it past Round 1, and also received the highest mean scores from judges.